Supplement 1: Different Response Distributions

### 2018-10-08 pkg/disttree/inst/draft/supplement/Rain_stationwise_results.Rnw
adapted to new results of variable importance
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2315 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: adebd8a052398e7be1f9bc0a7e9e68719d88191b

<<varimp, fig=TRUE, echo=FALSE, height=4, width=6.4>>=
par(mar = c(5, 10, 1, 2))
barplot(varimp10, horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Mean increase in CRPS",
        xlim = c(0,0.09))
axis(1, at = seq(0, ceiling(max(varimp10) * 5)/5, 0.02), las = 1, mgp = c(0, 1, 0))
@

>>>>

<<varimp, fig=TRUE, echo=FALSE, height=4, width=6.4>>=
par(mar = c(5, 10, 1, 2))
barplot(varimp10, horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Mean increase in CRPS",
        xlim = c(0,max(varimp10)))
axis(1, at = seq(0, ceiling(max(varimp10) * 5)/5, 0.02), las = 1, mgp = c(0, 1, 0))
@
